\section{Introduction}
\label{sec:intro}
Data mining can be used to solve many complex problems in modern computing, from determining the most.  Kaggle\footnote{A data science competition website.  http://kaggle.com} is a website that is home to many competitions that solve very complex and intriguing problems.  It allows companies such as Facebook, StackOverflow, and others post data science competitions for cash prizes.  The competition that is described in this report is job salary prediction, put on by an advertisement search company called Adzuna\footnote{http://adzuna.com}.  By predicting the salary from job posts, Adzuna can provide more accurate ads to their customers.\\

The competition is about predicting the salary of a job posting based on other attributes in the advertisement.  These attributes are described in detail in Section~\ref{sec:gathering}, and with these attributes we will apply algorithms to weigh and train our classifier, from over 240,000 training instances, and then test them on over 40,000 test instances.   We use multiple tools and algorithms to obtain a good classifier to this dataset.  Section~\ref{sec:dm} will go in detail about our algorithms and the tools used, as well as the motivation for them.  The scores obtained are measured by the classifier's \textit{Mean Absolute Error} (MAE), which is then compared to the rest of the world's submissions to rank them.\\

The process of our classification is as follows: Data Gathering, Data Preparation, and Data Mining.  Gathering consists of collecting the data and interpreting their meaning and schema.  Preparation is a large step, as the algorithms and tools require certain specific types of data and schemas, and getting the raw data to this state can be non-trivial, as in the case of a bag-of-words\footnote{Bag-of-words is a method of processing unstructured text into a dictionary, without grammar, punctuation, or language nuances} method of text processing. 